A mixture of hidden Markov models to predict the lymphatic spread in head and neck cancer depending on primary tumor location

### 2025-06-02 _tex/manuscript.tex
Built site for gh-pages

We first analyze the risk predictions for the case where we diagnosed

>>>>

We first analyze the risk predictions for the case where we clinically
diagnose no positive LNLs

\begin{minipage}{0.50\linewidth}

\includegraphics{figures/plot_C02_early_no_positive_diagnoses.png}

\subcaption{\label{fig-oral_cavity_no_pos_C02_early}}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\includegraphics{figures/plot_C03_early_no_positive_diagnoses.png}

\subcaption{\label{fig-oral_cavity_no_pos_C03_early}}

\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}

\includegraphics{figures/plot_C04_early_no_positive_diagnoses.png}

\subcaption{\label{fig-oral_cavity_no_pos_C04_early}}

\end{minipage}%
%
\begin{minipage}{0.50\linewidth}

\includegraphics{figures/plot_C05_early_no_positive_diagnoses.png}

\subcaption{\label{fig-oral_cavity_no_pos_C05_early}}

\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}

\includegraphics{figures/plot_C06_early_no_positive_diagnoses.png}

\subcaption{\label{fig-oral_cavity_no_pos_C06_early}}

\caption{\label{fig-oral_cavity_early_no_pos}Probability of occult
metastases in LNLs I, II, III, IV and V for early t-stages in oral
cavity subsites C02 (tongue), C03 (gum), C04 (floor of mouth), C05
(palate) and C06 (other parts of mouth). The red line marks the 5\%
threshold for high risk of involvement.}

In figure~\ref{fig-oral_cavity_early_no_pos} we can see that the model
predicts different risks of involvement for each subsite. For subsite
C03 (gum), predicts a higher risk of involvement for LNL I. In subsites
C02 (tongue) and C05 (palate), the model predicts an above threshold
risk of involvement for LNL II. While for subsites C02 (tongue) and C06
(other parts of mouth) all LNLs stay below the 5\% threshold. Thus, the
model would propose three different treatment plans for these subsites,
with C03 (gum) LNL I, C02 (tongue) LNL II and C05 (palate) LNL II being
irradiated, while C04 (floor of mouth) and C06 (other parts of mouth)
would not need elective irradiation at all, which is a major deviation
from the clinical guidelines which irradiate LNLs I, II and III for all
oral cavity subsites.
